%% This defines the bibliography file (main.bib) and the bibliography style.
%% If you want to create a bibliography file by hand, change the contents of
%% this file to a `thebibliography' environment.  For more information 
%% see section 4.3 of the LaTeX manual.
\begin{singlespace}
\bibliography{main}
\bibliographystyle{plain}

\begin{thebibliography}{9}

\bibitem{discreteqtasep}
  A.Borodin, I. Corwin,
  \emph{Discrete time q-TASEP},
  Int. Math. Res. Not. IMRN,
  2014,
  arXiv:1305.2972.

\bibitem{duality2014}
  A.Borodin, I. Corwin, and T. Sasamoto,
  \emph{From duality to determinants for q-TASEP and ASEP},
  Annals of Probability 2014,
  Vol. 42, No. 6, 2314-2382,
  2014,
  arXiv:1207.5035.

\bibitem{macdonald2014}
  A. Borodin, I. Corwin,
  \emph{Macdonald processes},
  Probability Theory and Related Fields,
  2014,
  arXiv:1111.4408.

\bibitem{tracy-widom-def}
  A. Borodin, I. Corwin, and P.L. Ferrari,
  \emph{Free energy fluctuations for directed polymers in random media in 1+1 dimention},
  Comm. Pure Appl. Math(2014),
  1129-1214

\bibitem{generator-duality}
  A. Vo\ss -B\"o hme, W. Schenk and A.-K. Koellner,
  \emph{On the equivalence between Liggett duality of Markov processes and the duality relation between their generators},
  Markov Processes and Related Fields,
  2011.

\bibitem{airy-kernel}
  Craig. A. Tracy and H. Widom,
  \emph{Level-spacing Distributions and the Airy Kernel},
  Comm. Math. Phys. 159 (1994),
  151-174.

\bibitem{special-functions}
  G. Andrews, R. Askey, R. Roy,
  \emph{Special functions},
  Cambridge University Press,
  2000.

\bibitem{phase2015}
  G. Barraquand,
  \emph{A phase transition for q-TASEP with a few slower particles},
  Stochastic Processes and Their Applications 125 (2015),
  pp. 2674-2699,
  2015,
  arXiv:1404.7409.

\bibitem{symmetrization}
  I.G. Macdonald,
  \emph{Symmetric functions and Hall polynomials},
  2nd edition, 
  Oxford University Press,
  New York,
  1999

\bibitem{interacting-particle-system}
  Liggett, T. M.,
  \emph{Interacting Particle Systems},
  Springer,
  Berlin,
  2005,
  MR2108619.

\bibitem{functional-analysis}
  P. D. Lax.,
  \emph{Functional Analysis},
  Wiley-interscience,
  2002.

\bibitem{asymptotics2013}
  P. L. Ferrari, B. Vet\H o,
  \emph{Tracy-Widom asymptotics for q-TASEP},
  Ann. Inst. H. Poincar\' e Probab. Stat.,
  2013,
  arXiv:1310.2515.

\end{thebibliography}

\end{singlespace}
